On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-07-20 paper_lap/JCP_response1/01intro.tex
updated files

 In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem. Our approach is based on using the discretization of a suitable adjoint problem. In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated. We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner. \upd{This approach generalizes naturally to three-dimensional problems, though efficient discretization of the corresponding Dirichlet problems is the subject of ongoing research. A similar analysis as in \cite{serkhacha} can be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}

>>>>

 In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem. Our approach is based on using the discretization of a suitable adjoint problem. In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated. We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner. \upd{This approach generalizes naturally to three-dimensional problems, though efficient discretization of the corresponding Dirichlet problems is the subject of ongoing research. A similar analysis as in \cite{serkhacha} can, in principle, be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}

### 2020-07-20 paper_lap/JCP_response1/04nprelim.tex
updated files

\subsection{Discretization of the Neumann problem}
In principle a similar method could be employed to discretize the Neumann boundary integral equations. Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range \upd{$(-1/2,1/2)$} makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles. When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$). Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult. Instead, a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.

>>>>

\subsection{Discretization of the Neumann problem}
In principle a similar method could be employed to discretize the Neumann boundary integral equations. Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range \upd{$(-1/2,1/2)$}) makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles. When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$). Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult. Instead, a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.

### 2020-07-20 paper_lap/JCP_response1/05apparatus.tex
updated files

\begin{remark}
\label{rem:far-field-accuracy}
We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than one panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ i.e. the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
\end{remark}
\begin{remark}
\label{rem:strong-sol-smooth}
Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately. This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner. The collection of singular powers arising in Neumann problems contain negative powers which are not contained in this set and hence are not interpolated accurately.
\end{remark}
{\color{blue}
\begin{remark}
In this approach, note that the discretization of the Neumann problem, inherits its spectral properties from the discretization of the corresponding adjoint Dirichlet problem (eigenvalues and singular values are the same, but eigenvectors and singular vectors may differ). Thus, when using an iterative method for solving the discrete linear system for the Dirichlet and Neumann problem, the number of iterations required for the relative residual to converge below $\varepsilon$ would be fairly similar. 
\end{remark}
}

@@

In light of this we consider the following integral equation
\upd{
\begin{align}\label{eqn:resolve_neum0}
-\frac{\sigma(s)}{2} + \int_{-2\delta}^{2\delta} k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
\end{align}
}
We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-2\delta,2\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
\upd{
\begin{align}\label{eqn:resolve_diri0}
-\frac{\sigma(s)}{2} + \int_{-2\delta}^{2\delta} k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta,
\end{align}}
which is a Dirichlet boundary integral equation for a wedge with a piecewise analytic right-hand side. In particular, we can discretize the operator using the method summarized in the previous section. Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{hoskins2019numerical} for a detailed description of the method). On the intervals $[-2\delta,-\delta]$ and $[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals. Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights. Let $\upd{\uA_0}$ be the discretization of the interior Dirichlet problem operator (i.e. the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})). We note that due to the scale invariance of Laplace's equation for polygonal domains the portion of $\upd{\uA_0}$ corresponding to the self-interaction of $L_0$ is a submatrix of the original matrix $\upd{\uA}.$ All other blocks can be generated using the discretization nodes as quadrature nodes.

>>>>

\begin{remark}
\label{rem:far-field-accuracy}
We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than one panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ i.e. the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
\end{remark}
\begin{remark}
\label{rem:strong-sol-smooth}
Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately. This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner. The collection of singular powers arising in Neumann problems contain negative powers which are not contained in this set and hence are not interpolated accurately.
\end{remark}
{\color{blue}
\begin{remark}
In this approach, note that the discretization of the Neumann problem inherits its spectral properties from the discretization of the corresponding adjoint Dirichlet problem (eigenvalues and singular values are the same, but eigenvectors and singular vectors may differ). Thus, when using an iterative method for solving the discrete linear system for the Dirichlet and Neumann problem, the number of iterations required for the relative residual to converge below $\varepsilon$ would be fairly similar. 
\end{remark}
}

@@

In light of this we consider the following integral equation
\upd{
\begin{align}\label{eqn:resolve_neum0}
-\frac{\sigma(s)}{2} + \int_{-2\delta}^{2\delta} k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
\end{align}
}
We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-2\delta,2\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
\upd{
\begin{align}\label{eqn:resolve_diri0}
-\frac{\sigma(s)}{2} + \int_{-2\delta}^{2\delta} k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta,
\end{align}}
which is a Dirichlet boundary integral equation for a wedge with a piecewise analytic right-hand side. In particular, we can discretize the operator using the method summarized in the previous section. Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{hoskins2019numerical} for a detailed description of the method). On the intervals $\upd{K_0}=[-2\delta,-\delta]$ and $\upd{Q_0}=[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals. Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights. Let $\upd{\uA_0}$ be the discretization of the interior Dirichlet problem operator (i.e. the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})). We note that due to the scale invariance of Laplace's equation for polygonal domains the portion of $\upd{\uA_0}$ corresponding to the self-interaction of $L_0$ is a submatrix of the original matrix $\upd{\uA}.$ All other blocks can be generated using the discretization nodes as quadrature nodes.

### 2020-07-20 paper_lap/JCP_response1/manuscript.tex
updated files

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
\upd{
In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary. Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}. Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$, the corresponding weights are given by $w_{1}, \ldots w_{N}$, $X = L^2({\Gamma})$, $\underline{X} = \mathbb{R}^{N}$, $\left< \cdot, \cdot \right>_{Y}$
denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$, and
$S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots, f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
\end{equation}
Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.

Let $A$ denote operator corresponding to the interior Dirichlet problem where the solution is represented as a double layer potential. Let $\underline{A}$ denote the $N\times N$ matrix corresponding to the discretization of $A$. Let $g$ denote the
right-hand side for the Neumann problem, and let $\sigma$ denote the corresponding solution.   Let $\underline{\sigma}$ denote the solution of the linear system $\uA^{T} \usigma = S[g]$. Let $h_{i}$, $i=1,2,\ldots M$, denote the scaled Legendre polynomials to the panel $\Gamma_{\ell}$.
The main result of this appendix is to show that under suitable assumptions, that the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
\begin{equation}
e = \max_{i=1,2\ldots, M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
\end{equation}

@@

But first, we present a lemma about the accuracy of Gaussian quadrature
\begin{lemma}
\label{lem:b1}
Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $L^{2}[-1,1]$, then the integral
$\int_{-1}^{1} p \cdot g$ can be computed accurately using Gaussian quadrature of any order greater than or equal to $M$.
As a consequence, For any $g$ in $\L^{2}(\Gamma)$, then 
\begin{equation}
\left<h_{i},g \right>_{X} = \left< S[h_{i}], S[g] \right>_{\uX}
\end{equation}
\end{lemma}

>>>>

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
\upd{
In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary. Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}. Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$, the corresponding weights are given by $w_{1}, \ldots w_{N}$, $X = L^2({\Gamma})$, $\underline{X} = \mathbb{R}^{N}$, $\left< \cdot, \cdot \right>_{Y}$
denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$, and
$S:X \to \uX$ denotes the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots, f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
\end{equation}
Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to its piecewise interpolant on the boundary.
Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.

Let $A$ denote operator corresponding to the interior Dirichlet problem where the solution is represented as a double layer potential. Let $\underline{A}$ denote the $N\times N$ matrix corresponding to the discretization of $A$. Let $g$ denote the
right-hand side for the Neumann problem, and let $\sigma$ denote the corresponding solution.   Let $\underline{\sigma}$ denote the solution of the linear system $\uA^{T} \usigma = S[g]$. Let $h_{i}$, $i=1,2,\ldots M$, denote the scaled Legendre polynomials to the panel $\Gamma_{\ell}$.
The main result of this appendix is to show that under suitable assumptions the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
\begin{equation}
e = \max_{i=1,2\ldots, M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
\end{equation}

@@

Before doing so, we first state a lemma about the accuracy of Gaussian quadrature.
\begin{lemma}
\label{lem:b1}
Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $L^{2}[-1,1]$, then the integral
$\int_{-1}^{1} p \cdot g$ can be computed accurately using Gaussian quadrature of any order greater than or equal to $M$.
As a consequence, For any $g$ in $\L^{2}(\Gamma)$, then 
\begin{equation}
\left<h_{i},g \right>_{X} = \left< S[h_{i}], S[g] \right>_{\uX}
\end{equation}
\end{lemma}
